---
title: "Ghana Visit - Top spots"
author: "Ramy Hashem"
date: "November 11, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

## Leaflet Maps

In this module, I created a map of my city of residence Accra - Ghana.  
I've listed my top spots out of 3 years living here.

I've created layers on the map for the following:  
1. Outings, restaurants (my favorite ones in Accra)  
2. Top attractions and sight seeing  
3. My Office location (Nokia Networks)  

#### Note:   
1- *Click on Icons to see my comments*  
2- *Click on layer 'top right' to show/hide groups*  

```{r maps}
library(leaflet)

# Read csv file
maps <- read.csv(file = "data.csv")

# Load the icons for 3 different groups
maps_icon <- iconList(Work = makeIcon("office.png",,24,24,24,24), Outings=makeIcon("restaurant.png",,24,24,24,24), Sights = makeIcon("sight.png",,24,24,24,24))

# Load the map from the file. with Labels and different icons
maps %>% leaflet() %>% addTiles() %>% addMarkers(label=~Item, popup = ~Description, icon = ~maps_icon[Group], group = ~Group) %>% addLayersControl(overlayGroups = ~Group, options = layersControlOptions(collapsed = FALSE))

```
